---
title: "p8105_hw1_sl5009"
author: "Shengzhi Luo"
date: "28/09/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,echo=FALSE,message=FALSE}
library(tidyverse)
```
##Problem 1

Let's create a data frame.

```{r}
hw1_df = tibble(
  random_sample =rnorm(10) ,
  random_sample_pos = random_sample > 0,
  vec_char = c("s","h","e","n","g","z","h","i","l","u"),
  vec_factor = factor(c("birth", "birth", "age",
                        "age","height","age","birth","height","birth","age"))
)
hw1_df
```

Now we try to take teh mean of each variable.
```{r}
#mean of numeric variable
mean(pull(hw1_df,random_sample))
```

```{r}
#mean of logical variable
mean(pull(hw1_df,random_sample_pos))
```

```{r}
#mean of character vector
mean(pull(hw1_df,vec_char))
```

```{r}
#mean of factor vector
mean(pull(hw1_df,vec_factor))
```

As shown above, numeric variables and logical variables can have mean while character variables and factor varibles don't have mean.

```{r,eval=FALSE}
##Apply as.numeric function
num_log <- as.numeric(pull(hw1_df,random_sample_pos))
num_char <-as.numeric(pull(hw1_df,vec_char))
num_factor<-as.numeric(pull(hw1_df,vec_factor))

```

The character variables still can't be numeric unless numbers involved in the character vector and that's why we can't have mean of these variables. Factor vector can be converted into numeric varibales. Although the numbers they converted can be arbitrary numbers, there are also no mean for factor variables.